Presolving for\\ Mixed-Integer Semidefinite Optimization

### 2020-12-14 tex/MISDP-Presolving/MISDPpresolving.tex
refine description a bit

@@

It might be instrumential to look at the linear analogue:
\[
  S \define \{(x,z) \in \R_+^n \times [0,1]^n \suchthat \sum_{i=1}^n x_i =
  1,\; \sum_{i=1}^n z_i \leq k,\; 0 \leq x_i \leq z_i \;\forall\, i \in [n]\}.
\]
This is related to the \emph{hypersimplex}
\[
  \Delta_{n,k} \define \conv \{z \in \{0,1\}^n \suchthat \sum_{i=1}^n z_i = k\},
\]
for which complete linear descriptions are available, see
Ziegler~\cite{Zie95}.

\begin{question}
  Does this give a linear description of $S$ and can this be extended to
  the SDP case?
\end{question}

>>>>

Indeed, it is NP-hard to optimize over $S_I$ -- this is goal of the
RIP-problem.

@@

It might be instrumential to look at the linear analogue:
\[
  S \define \{(x,z) \in \R_+^n \times [0,1]^n \suchthat \sum_{i=1}^n x_i =
  1,\; \sum_{i=1}^n z_i \leq k,\; 0 \leq x_i \leq z_i \;\forall\, i \in [n]\}.
\]
Both the polytopes
$\{x \in \R^n \suchthat \ones\T x = 1,\; 0 \leq x \leq z\}$ for fixed
$z \in \{0,1\}^n$ and
$\{z \in \R^n \suchthat \ones\T z \leq k,\; x \leq z\}$ for fixed
$x \in \{0,1\}^n$ are integral.

\begin{question}
  Is the above description integral?
\end{question}
